Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-16 paper/v1.0/sections/1_introduction.tex
Add more reference paper

Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics [15].
Quantum optics have dragged research attention in the disciplines of optoelectronics [1,2,3], sensing [4,5,6], energy harvesting [7,8], quantum computing [9,10,11], bio-information [12,13], and abundant affiliates of recent technologies [14]. 
The studies on quantum optics of nanostructures were centered on metamaterials [28,34], quantum plasmonic effects [27,33], lasers and amplifiers [29,30], quantum cavity physics [31,32]. However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics [16-24]. 
The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance [35].
Among these works, most studies have considered the driving field as a perturbative field [18,20] that is not applicable for systems under high-intensity illumination [24,25]. When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase. Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) [18,36,37]. On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
A theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref. [22,18,24] where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref. [24], introducing a novel type of Green’s functions namely four-times Green’s functions. As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.

@@

In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels [49].
Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [24].
Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model [47] already developed for specialised quantum Hall systems that have been considered without the external dressing field.  
Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we belive that our theoritical analysis and visual depictions of results can be used to undestand the basic structure and optimize the performance of optical manipulation of trasport propeties in a two-dimentional quantum Hall system.

>>>>

Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
Quantum optics have dragged research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant affiliates of recent technologies \cite{rivera20}. 
The studies on quantum optics of nano-structures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}. However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics [16-24]. 
The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance [35].
Among these works, most studies have considered the driving field as a perturbative field [18,20] that is not applicable for systems under high-intensity illumination [24,25]. When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase. Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) [18,36,37]. On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
A theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref. [22,18,24] where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref. [24], introducing a novel type of Green’s functions namely four-times Green’s functions. As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.

@@

In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels [49].
Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [24].
Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model [47] already developed for specialised quantum Hall systems that have been considered without the external dressing field. 
Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we belive that our theoritical analysis and visual depictions of results can be used to undestand the basic structure and optimize the performance of optical manipulation of trasport propeties in a two-dimentional quantum Hall system.

### 2021-07-16 paper/v1.0/sections/8_manipulate_conductivity.tex
Add more reference paper

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{\label{fig_4} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_6}
\caption{\label{fig_5} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}

>>>>

\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_6}
\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}
